Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-02-05 manuscript.tex
bibliography update

Despite some studies of seismicity rates and attempts at defining the main seismic zones \citep{berrocal_1984}, 2000, Assumpção in \citep{talwani_2014} (REFERENCE), Brazil has no seismic hazard map at national scale.

@@

\subsection{Previous Smoothing Seismicity (Frankel, Woo, Helmstetter\ldots)}

>>>>

Despite some studies of seismicity rates and attempts at defining the main seismic zones \citep{berrocal_1984, berrocal_1996, assumpcao_et_al_2014}, Brazil has no seismic hazard map at national scale.

@@

\subsection{Smoothing Seismicity}
